Comment: Reasoning about Interference Between Units

### 2015-08-04 paper/paper.tex
Adding the abstract and titlepage to paper.tex. Also struggling with weeird errors related to the acknowledgements, I think, to no avail.

\documentclass[12pt]{article}
\RequirePackage{snapshot}

\author{Peter Aronow \thanks{Assistant Professor, Dept of Political Science,
    Yale University \textit{Acknowledgements:} } \and Jake Bowers \thanks{Associate Professor, Dept of Political
    Science and Statistics, University of Illinois @ Urbana-Champaign
    (\texttt{jwbowers@illinois.edu}).} \and Mark Fredrickson \thanks{Ph.D. Student in Statistics and Political Science, University of Illinois @ Urbana-Champaign.}}

  \date{\today}

\usepackage{../styles/common}

%%% Paper specific packages
\usepackage{setspace}
\usepackage[letterpaper,bottom=1in,top=1in,right=1in,left=1in,includemp=FALSE]{geometry}
\usepackage{microtype} %only useful with pdflatex

@@

% \ifanon
% \footnote{We are awesome!}
% \else
% \fi

\begin{document}
\VerbatimFootnotes
\input{titlepage}
%\setstretch{1.6} %1.6 or 1.37 which I think is "true double spacing"
%\onehalfspacing
%%I don't think I need to double space footnotes for AJPS. Check this.
\abovedisplayshortskip=0pt
\belowdisplayshortskip=0pt
\abovedisplayskip=0pt
\belowdisplayskip=0pt
%\tableofcontents

% include stuff here!
% include stuff here!

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

>>>>

\documentclass[12pt]{article}
\RequirePackage{snapshot}
\usepackage{../styles/common}

\author{Jake Bowers \thanks{Associate Professor, Dept of Political Science and Statistics, University of Illinois @ Urbana-Champaign (\texttt{jwbowers@illinois.edu}).} \and Mark Fredrickson \thanks{Ph.D. Student in Statistics and Political Science, University of Illinois @ Urbana-Champaign.} \and Peter M. Aronow \thanks{Assistant Professor, Dept of Political Science and Biostatistics, Yale University}}

%%% Paper specific packages
\usepackage{setspace}
\usepackage[letterpaper,bottom=1in,top=1in,right=1in,left=1in,includemp=FALSE]{geometry}
\usepackage{microtype} %only useful with pdflatex
\usepackage{fancyvrb} % for verbatim text in footnotes

@@

% \ifanon
% \footnote{We are awesome!}
% \else
% \fi
%% \abovedisplayshortskip=0pt
%% \belowdisplayshortskip=0pt
%% \abovedisplayskip=0pt
%% \belowdisplayskip=0pt
%% 
\begin{document}
\VerbatimFootnotes

\begin{titlepage}

\maketitle

\begin{abstract} 
\citet{bowers2013sutva} showed that one could use Fisher's randomization-based
hypothesis testing framework to assess counterfactual causal models of
treatment propagation and spillover across social networks.  This research
note improves the statistical infernce presented in \citet{bowers2013sutva}
(henceforth BFP) by substituting a test statistic based on a sum of squared
residuals and incorporating information about the fixed network for the simple
the Kolmogorov-Smirnov test statistic  \citep[\S 5.4]{MylesHollander1999a}
that they used. The point of this short article is to incrementally improve
the use of BFP's ``reasoning about interference'' approach. We do not offer
results about test statistics for multi-parameter causal models on social
networks here, but instead hope that this research note stimulates further,
and deeper, work on test statistics and sharp hypotheses.
\end{abstract}

Key Words: Causal effect; Interference; Randomized experiment;
Randomization inference; Fisher's Sharp Null Hypothesis; SUTVA

\end{titlepage}

%\input{titlepage.tex}
%\setstretch{1.6} %1.6 or 1.37 which I think is "true double spacing"
%\onehalfspacing

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "paper"
%%% End:
